An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-22 EconGrowth2.Rnw
Added CES spaghetti graphs.

**** Replace Figure~\ref{fig:CES_GDP_Lattice_Graph} with four graphs that show
the range of predictions from resamples with each nesting. ****

@@

>>>>

@@

The resample model predictions for each nesting 
in Figure~\ref{fig:CES_GDP_Lattice_Graph} can be shown as gray lines 
beneath superimposed on the historical data as shown
in Figures~\ref{fig:CES_Spaghetti_Graph_kl}--\ref{fig:CES_Spaghetti_Graph_ekl}. 
Figure~\ref{fig:CES_Spaghetti_Graph_kl} shows CES model resample predictions
for the ($kl$) nesting (without energy).

<<CES_Spaghetti_Graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Graph of CES resample model indexed GDP predictions for the ($kl$) nesting (without energy). Only 50 resample models are shown. **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
createCESSpaghettiGraph(energyType=NA)
@

Figure~\ref{fig:CES_Spaghetti_Graph_kle} shows CES model 
resample predictions for the ($kl$)$e$ nesting.

<<CES_Spaghetti_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Graph of CES resample model indexed GDP predictions for the ($kl$)$e$ nesting (with energy). Only 50 resample models are shown. **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
createCESSpaghettiGraph(energyType="Q", nest="(kl)e")
@

<<CES_Spaghetti_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Graph of CES resample model indexed GDP predictions for the ($le$)$k$ nesting (with energy). Only 50 resample models are shown. **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
createCESSpaghettiGraph(energyType="Q", nest="(le)k")
@

<<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Graph of CES resample model indexed GDP predictions for the ($ek$)$l$ nesting (with energy). Only 50 resample models are shown. **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
createCESSpaghettiGraph(energyType="Q", nest="(ek)l")

@
